Combining formal and distributional models of predicate semantics

### 2016-03-03 paper/paper.tex
adding tacl2015 paper
Former-commit-id: 0d96938966b2ba3d3b01c8b2bbda93814689193d
Former-commit-id: ebd9e90a03480ed7f01706ac6735016816934591
Wrote the evaluation section.
Mostly just the method and discussion sections left for the initial draft.


Former-commit-id: 5c44bff5d621f101c472a1832e1ee5e1156ee9a6
Former-commit-id: 03a29a4634ebf13fc62f936d117861489d88b87b

@@

We use the dataset introduced by Krishnamurthy and
Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary}, which
consists of the ClueWeb09 web
corpus\footnote{http://www.lemuproject.org/clueweb09.php} along with Google's
FACC entity linking of that corpus to
Freebase~\cite{gabrilovich-2013-clueweb-entity-linking}.  3 million webpages
from this corpus were processed with a CCG parser to produce logical forms, as
described in \secref{jayant-semparse}.  This produced 2.1m predicate instances
involving 142k entity pairs and 184k entities.  After removing
infrequently-seen predicates (seen fewer than 6 times), there were 25k
categories and 4.2k relations.\footnote{The differences in numbers reported
here versus those reported by Krishnamurthy and
Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary} are due to the
improved logical form generation, discussed in \secref{better-lfs}.}

@@

\subsection{Models}

@@

>>>>

\subsection{Candidate entity generation}
\label{sec:better-candidates}

@@

We use the dataset introduced by Krishnamurthy and
Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary}, which
consists of the ClueWeb09 web
corpus\footnote{http://www.lemuproject.org/clueweb09.php} along with Google's
FACC entity linking of that corpus to
Freebase~\cite{gabrilovich-2013-clueweb-entity-linking}.  For training data, 3
million webpages from this corpus were processed with a CCG parser to produce
logical forms, as described in \secref{jayant-semparse}.  This produced 2.1m
predicate instances involving 142k entity pairs and 184k entities.  After
removing infrequently-seen predicates (seen fewer than 6 times), there were 25k
categories and 4.2k relations.\footnote{The differences in numbers reported
here versus those reported by Krishnamurthy and
Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary} are due to the
improved logical form generation, discussed in \secref{better-lfs}.}

We also used the test set created by Krishnamurthy and Mitchell, which contains
220 queries generated in the same fashion as the training data from a separate
section of ClueWeb.  However, we used this set for intermediate evaluations
while developing our models, and so we also generated another, similar test set
from a different held out section of ClueWeb.  This final test set contains 307
queries.  We report results on both of these test sets below.  All of the data
used in these experiments is available at [url withheld for review].

\subsection{Experiments}

We compare three models in our experiments: a distributional-only model, a
formal-only model, and our proposed model, which is both distributional and
formal.  The distributional-only model is the model proposed by Krishnamurthy
and Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary} and
described in \secref{jayant-semparse}.  The combined model is the model
described in \secref{sec:formal-and-distributional}, while the formal-only
model removes the distributional component from the combined model (i.e., all
parameters $\theta$ and $\phi$ from the distributional portion of the model are
fixed at zero during training and test).  Note that this formal-only baseline
is also new to this work---we are not aware of any other work that models
language in terms of features derived from a formal knowledge base.

In addition to running experiments comparing these three models on the two test
sets described above, we also evaluated the improvement gained by using our
modified logical forms (\secref{better-lfs}), and our entity proposal mechanism
(\secref{better-candidates}).

@@

Given a fill-in-the-blank query such as ``Italian architect \blank{}'', each
system produces a ranked list of 100 candidate entities.  To compare the output
of the systems, we follow a pooled evaluation protocol commonly used in
relation extraction and information
retrieval~\cite{west-2014-kbc-via-qa,riedel-2013-mf-universal-schema}.  We take
the top 30 predictions from each system and manually annotate whether they are
correct, and use those annotations to compute the average precision (AP) and
reciprocal rank (RR) of each system on the query.  Average precision is defined
as $\frac{1}{m}\sum^m_{k=1} \mathrm{Prec}(k) \times \mathrm{Correct}(k)$, where
$\mathrm{Prec}(k)$ is the recision at rank $k$, $\mathrm{Correct}(k)$ is an
indicator function for whether the $k$th answer is correct, and $m$ is number
of returned answers (up to 100, in this evaluation).  Reciprocal rank is
computed by first finding the rank $r$ of the first correct prediction made by a
system.  Reciprocal rank is then $\frac{1}{r}$, ranging from 1 (if the first
prediction is correct) to 0 (if there is no correct answer returned).  In the
tables below we report \emph{mean} average precision (MAP) and reciprocal rank
(MRR), averaged over all of the queries in the test set.  We also report a
weighted version of MAP, where the AP of each query is scaled by the number of
annotated correct answers to the query.

@@

\begin{table}
  \centering
  \begin{tabular}{|l|r|r|}
    \hline
    Method & MAP & MRR \\
    \hline
    Distributional-only & .239 & ?? \\
    Distributional-only (old lfs) & ?? & ?? \\
    \hline
    Formal-only & ?? & ?? \\
    Formal-only (old lfs) & ?? & ?? \\
    \hline
    Combined model & \textbf{.340} & ?? \\
    Combined model (old lfs) & ?? & ?? \\
    \hline
  \end{tabular}
  \caption{Results on the development set for our fill-in-the-blank task.  The
  combined model improves MAP by 42\% compared to the distributional-only
  baseline.  Additionally, the improved logical forms presented in
  \secref{better-lfs} significantly improve all models.}
  \label{tab:dev-results}
\end{table}

\tabref{dev-results} shows the results of our experiments on the development
set (the same as the test set used by Krishnamurthy and
Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary}).  As can be
seen, the combined model significantly improves performance, giving a 42\%
relative increase in MAP over the distributional-only baseline.  This table
also shows the benefit of using our modified logical forms (see
\secref{better-lfs}); by being able to better model the relations between
entities, MAP of all of the models is significantly improved.

\begin{table}
  \centering
  \begin{tabular}{|l|r|r|}
    \hline
    Method & MAP & MRR \\
    \hline
    Distributional-only & .231 & ?? \\
    \ \ \ -related entities & .170 & ?? \\
    \hline
    Formal-only & ?? & ?? \\
    \hline
    Combined model & \textbf{.376} & ?? \\
    \hline
  \end{tabular}
  \caption{Results on the final test set for our fill-in-the-blank task.  The
  combined model improves MAP by 63\% relative to the distributional-only
  baseline.  Additionally, allowing the distributional-only model to use
  Freebase to propose candidates improves MAP by 6 points absolute due to
  improved recall.}
  \label{tab:final-results}
\end{table}

\tabref{final-results} shows that these improvements are consistent on the
final test set, as well.  The performance improvement seen by the combined
model is actually larger on this set, going from a MAP of .231 to .376, a 63\%
relative improvement.  In this table, we also show the improvement gained by
allowing the distributional-only model to propose candidate entities that are
related in Freebase (see \secref{better-candidates}).  Even though these
candidates are always ranked at the bottom of the list of predictions (with a
score of 0), the additional recall provided by being able to propose more
entities raises MAP of the distributional-only model from .170 to .231.
